---
title: "group_document.qmd"
format: html
editor: visual
---

## Laura

Holaa

```{r}
#first

```

```{r}
#second

```

## Chen

-   **T1:** Find the `GitHub` repository for the `ggplot2` R-package

-   **Q1:** How many Contributors are there?

    295

-   **T1:** Find the `GitHub` repository for the `Linux kernel`

-   **Q2:** How many Contributors are there?

    5000+

-   **Q3:** Discuss in your group why having an organised approach to version control is central? And consider the simple contrast of the challenges you were facing when doing the course assignments.

This matters because, first of all, files are organised and reproducible and, second, you can go back and regenerate a former version if anything goes wrong. This would have been nice for collaborating, so that everyone shares the same final document.

-   **Q4:** Discuss in your group, what happened and why? Try copying the message and paste it into google, did you get any hits?

R doesn't have our GitHub credentials and we should use the access token instead of the password

## Hongjin

yes captain

```{r}
library(ggplot2)
```

#### new analysis

```{r}
library(tidyverse)
```

## Sebastian

-   **T1:** Find the `GitHub` repository for the `ggplot2` R-package

-   **Q1:** How many Contributors are there?

    295

-   **T1:** Find the `GitHub` repository for the `Linux kernel`

-   **Q2:** How many Contributors are there?

    5000+

-   **Q3:** Discuss in your group why having an organised approach to version control is central? And consider the simple contrast of the challenges you were facing when doing the course assignments.

This matters because, first of all, files are organised and reproducible and, second, you can go back and regenerate a former version if anything goes wrong. This would have been nice for collaborating, so that everyone shares the same final document.

-   **Q4:** Discuss in your group, what happened and why? Try copying the message and paste it into google, did you get any hits?

R doesn't have our GitHub credentials and we should use the access token instead of the password

## Celina
